\chapter*{研究業績}
\addcontentsline{toc}{chapter}{研究業績}
\textbf{ポスター発表}
\begin{easylist}[itemize]
@ \underline{Soh Ishiguro}, Kazuharu Arakawa, Masaru Tomita. \textbf{"Benchmarking test for the detection methods of RNA editing sites based on RNA-seq data"}, MBSJ2013 (the 36th Annual Meeting of the Molecular Biology Society of Japan), Kobe, Japan (Dec. 3-6, 2013)

@ \underline{Soh Ishiguro}, Kazuharu Arakawa, Masaru Tomita. \textbf{"Benchmarking test for the detection methods of RNA editing sites based on RNA-seq data"}, NGS Field the 3rd Meeting, Kobe, Japan (Sep. 4-5, 2013)

@ Yuki Yoshida, \underline{Soh Ishiguro}, Kazuharu Arakawa, Takekazu Kunieda, Hirokazu Kuwabara, Daiki Horikawa, Atsushi Toyota, Toshiaki Katayama, Fujiyama Akisao, Masaru Tomita. \textbf{"RNA-Seqデータ用いたヨコヅナクマムシにおける細胞防御・修復関連遺伝子の同定"}, NGS Field the 3rd Meeting, Kobe, Japan (Sep. 4-5, 2013)

@ \underline{Soh Ishiguro}, Kazuharu Arakawa, Takekazu Kunieda, Hirokazu Kuwahara, Daiki D. Horikawa, Atsushi Toyoda, Toshiaki Katayama, Asao Fujiyama, Masaru Tomita. (2012) \textbf{"Identification of RNA editing sites in tardigrade transcriptome from RNA-Seq data"}, MBSJ2012 (the 35th Annual Meeting of the Molecular Biology Society of Japan), Fukuoka, Japan (Dec. 2-7, 2012)

@ \underline{Soh Ishiguro}, Kazuharu Arakawa, Takekazu Kunieda, Hirokazu Kuwahara, Daiki D. Horikawa, Atsushi Toyoda, Toshiaki Katayama, Asao Fujiyama, Masaru Tomita. (2012) \textbf{"Identification of RNA editing sites in tardigrade transcriptome from RNA-Seq data"}, CBI/JSBi/Omix2012 (Joint Conference on Informatics in Biology, Medicine and Pharmacology), Tokyo, Japan (Oct. 14-17)

@ Nobuaki Kono, Kazuharu Arakawa, Kazuki Oshita, Gembu Maryu, \underline{Soh Ishiguro}, Taiyo Miyashita, Hidetoshi Itaya, Yuki Yoshida, Masaru Tomita. (2012) \textbf{"Web Application for Pathway Visualization with Instinctive Interface for Metagenome data"}, CBI/JSBi/Omix2012 (Joint Conference on Informatics in Biology, Medicine and Pharmacology), Tokyo, Japan (Oct. 14-17)

@ \underline{石黒宗}, 荒川和晴, 冨田勝. (2012) \textbf{"次世代シーケンサーを用いたヨコヅナクマムシにおけるRNA editingの解析"}, 第2回NGS現場の会, 大阪, 日本 (2012年9月4日-6日)
\end{easylist}


\textbf{口頭発表}
\begin{easylist}[itemize]
@ \underline{石黒宗}, 荒川和晴, 冨田勝. (2013) \textbf{"ヨコヅナクマムシの乾眠メカニズムの研究"}, 慶應義塾大学 SFC Open Research Forum 2013, 東京, 日本 (2013年11月22-23日)
\end{easylist}